Paper One Summary

### 2015-09-01 paper/one/summary.tex
extended definitions
added related work to paper summary

\author{Matthew Neal, Joseph Sankar, and Sasha Sobran}

@@

\section*{Important Keywords}
\begin{description}
\item [{Ecological~inference}] The idea that an observation or finding
at an aggregated level can apply at a disaggregated level. For example,
the idea that a model of defects at the package level also applies.
at the file level
\item [{Ecological~fallacy}] An incorrect application of ecological inference. A discrepency between the findings at an aggregated level and disaggragated level.
For example, an instance where a model of defects at the product level
is incorrectly used to model defects at the file level.
\item [{Scale}] Size of an aggregated unit. THe larger the scale the bigger and fewer the aggregated units.
\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering.
\end{description}

\section*{Feature Extraction}
\begin{description}
\item [{1~-~Motivational~Statements}] Modern software applications are
composed of many files. Thus, the files are usually organized into
units, which may themselves be organized into broader units. While
research could be focused at the most granular level, for example
files, methods, even lines of code, research at these levels is costly
and takes time, so research instead usually examines data at higher
levels. Therefore, it would be useful to draw conclusions from higher
levels that would apply to lower levels.
\end{description}

>>>>

\author{Matthew Neal, Joseph Sankar, and Alexander Sobran}

@@

\section*{Important Keywords}
\begin{description}
\item [{Ecological~inference}] The idea that an observation or finding
at an aggregated level can apply at a disaggregated level. For example,
the idea that a model of defects at the package level also applies.
at the file level
\item [{Ecological~fallacy}] An incorrect application of ecological inference. A discrepency between the findings at an aggregated level and disaggragated level.
For example, an instance where a model of defects at the product level
is incorrectly used to model defects at the file level.
\item [{Scale}] Size of an aggregated unit. The larger the scale the bigger and fewer the aggregated units. This can effect affect the quality of statistical models built for defect prediction.
\item [{Zonation}] The manner in which aggregation is performed. For example, gerrymandering. This can create internal validity threats and lead to ecological fallacies.
\end{description}

\section*{Feature Extraction}
\begin{description}
\item [{1~-~Motivational~Statements}] Modern software applications are
composed of many files. Thus, the files are usually organized into
units, which may themselves be organized into broader units. While
research could be focused at the most granular level, for example
files, methods, even lines of code, research at these levels is costly
and takes time, so research instead usually examines data at higher
levels. Therefore, it would be useful to draw conclusions from higher
levels that would apply to lower levels.
\item [{4~-~Related Work}] To improve model performance, Koru \textit{et al.} recommend aggregating. Their methods to acheive improved performance include summing method-level measures into class-level measures and combining these with metrics from class-level features. They conclude that this approach overcomes the issues of asymmetry in defect data sets. Schr\"{o}ter \textit{et al.} conclude that predicting at coarser granularities is less difficult in comparison to finer granularities but lead to worse results. Zimmerman \textit{et al.} find different results where package level correlations and model correlations are higher than file level correlations and model correlations. Ambrose \textit{et al.} argue against the use of aggregate level metrics, though without data, stating predictions are more cumbersome to investigate,classes are inherently self-contained, and information derived from the package-level cannot be applied to the class level.
\end{description}
